Scattering Auditory Scenes for Classification: Supervised and Unsupervised Approaches

### 2016-06-24 paper/structureScene.tex
formula for the center frequencies
try reformulating the title
Scattering Auditory Scenes for Classification: Supervised and
Unsupervised Approaches

\begin{document}
%
% paper title
% can use linebreaks \\ within to get better formatting as desired
% Do not put math or special symbols in the title.
%\title{An evaluation framework for event detection using a morphological model of acoustic scenes}
\title{Acoustic Scene Classification: \\ Supervised and Unsupervised Approaches using the Scattering Transform}

@@

\cite{Anden2015}
Since it operates over a complex-valued input, the filterbank over log-frequencies $\gamma_1$ must cover the whole Fourier spectrum, including negative frequencies and the null frequency, to ensure invertibility and energy conservation.

@@

\section{Supervised approach}

>>>>

\begin{document}
%
% paper title
% can use linebreaks \\ within to get better formatting as desired
% Do not put math or special symbols in the title.
%\title{An evaluation framework for event detection using a morphological model of acoustic scenes}
\title{Scattering Auditory Scenes for Classification: Supervised and Unsupervised Approaches}

@@

\cite{Anden2015}
Since it operates over a complex-valued input, the filterbank over log-frequencies $\gamma_1$ must cover the whole Fourier spectrum, including negative frequencies and the null frequency, to ensure invertibility and energy conservation.
Therefore, wavelets on $\gamma_1$ have center frequencies of the form
$\theta_{\mathrm{fr}}  2^{-\gamma_{\mathrm{fr}}/Q_{\mathrm{fr}}}$, where $\gamma_{\mathrm{fr}}$ takes integer values betwen $0$ and $(J_\mathrm{fr} \times Q_\mathrm{fr} - 1)$ and $\theta_{\mathrm{fr}} = \pm 1$.

@@

\section{Supervised approach: support vector machines}
Support vector machines are large-margin binary discriminators with tunable regularization of misclassified examples.
